The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-07 manuscript/manuscript.Rnw
discuss the rodent specific lineage

\subsection{Rodentia}

\subsubsection{Mouse Placenta Transcriptome}

>>>>

\subsection{Rodentia Placenta Transcriptomes}

\begin{table}
  \tiny
<<rodentia.lineage.specific,echo=FALSE,results="asis">>=
rod.all.lin.spec <- placenta.lineage.specific.table("rod.all")
setkey(rod.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in the Rodentia
  order as compared to all other analyzed species.}
\label{tab:rodentia_lineage_specific}
\end{table}

We examined the expression of three rodentia, \mouse, \carmeli, and
\galili{}. We lacked sufficient power to detect any significant
changes on the Rodentia lineage in comparison to all other analyzed
species (\cref{tab:rodentia_lineage_specific}).

\subsubsection{\mouse Placenta Transcriptome}
